% Report for the NLP course project P6 The Apprentice Model
% Based on the Springer Nature article template

\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}

\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{url}
\usepackage{listings}


\raggedbottom

\begin{document}

\title[The Apprentice Model for Toxicity Detection]{Distilling an LLM Teacher into a Compact Transformer for Toxic Comment Classification}

\author{\fnm{Vadim} \sur{Sokolov}}

\affil{\orgdiv{Master's Degree in Computer Science}, \orgname{Universit\`a degli Studi di Milano}, \orgaddress{\city{Milan}, \country{Italy}}}

\abstract{This project studies knowledge distillation for Natural Language Processing through an ``apprentice model''. 
The goal is to investigate if a compact student model can imitate the decision behaviour of a larger teacher model on a specific text classification task.
The selected task is toxic comment classification. 
The experimental pipeline compares a classical TF-IDF and Logistic Regression baseline, a supervised BERT-base teacher trained on original dataset labels, a supervised BERT tiny student model.
An LLM OpenAI teacher was used to relabel a controlled subset of examples. 
On the natural distribution test split, the TF-IDF baseline got an F1 score of 0.406 at the default threshold of 0.5, while the supervised BERT-base teacher obtains an F1 score of 0.62.
Based on validation performance, the thresholds of 0.52 were selected for TF-IDF and 0.49 for BERT-base, but did not improve test F1 in either case.
The final distilled student achieves an F1 score of 0.696 against teacher labels. It shows partial imitation of the teacher's decision boundary.
The OpenAI teacher is much slower to query in the measured labelling pipeline, while the distilled student provides a compact local approximation for the selected toxicity classification task.}

\keywords{Natural Language Processing, Knowledge Distillation, Toxicity Detection, BERT, TF-IDF, Large Language Models, GPT}

\maketitle

\section*{Generative AI disclaimer}

Generative AI, specifically GPT-5.5, was used during the project implementation to validate the overall approach, suggest ideas for improving the experimental results, check the grammar of the report, create LaTeX tables, generate experiment configuration files, generate code documentation with comments, and help resolve Python package conflicts in the virtual environment.

\section{Introduction}\label{sec:introduction}

Large language models have demonstrated strong performance across many Natural Language Processing tasks, including classification, question answering, summarisation, and reasoning.
However, their size and computational cost make them difficult to utilize in constrained environments, especially when the target application requires limited resources.
Knowledge distillation resolves this problem by transferring knowledge from a larger teacher model to a smaller student model \cite{hinton2015distilling}.
Instead of trying to reproduce the full generality of the teacher, the student can be trained to imitate the teacher's behaviour on a specific task or domain.

This project explores this idea in the context of toxic comment classification. Toxicity detection is a relevant NLP task because it combines text classification, contextual language understanding, and ethical considerations related to bias, moderation, and disagreement.
The task is also appropriate for studying the tradeoff between model performance and efficiency. A large LLM may provide high quality judgments but it's slow and expensive to use.
Meanwhile, a compact model can be executed locally and quickly.

The project investigates if a compact Transformer model can be used as a lightweight student of a larger teacher model.
The selected student is BERT-tiny, a small Transformer encoder.
The teacher labelling stage uses an OpenAI LLM to classify examples and provide confidence scores.
In addition, a classical TF-IDF and Logistic Regression model is used as a baseline, connecting the project to traditional vector space methods covered in the course.

The relevant literature includes the original formulation of knowledge distillation by Hinton et al. \cite{hinton2015distilling}, where a student model learns from softened teacher output distributions and Transformer based language models such as BERT \cite{devlin2019bert}.
TinyBERT \cite{jiao2020tinybert} demonstrate that smaller Transformer models can preserve part of the performance of larger models, reducing computational cost. 
This project applies the same general motivation to a practical toxicity detection pipeline and evaluates the resulting trade offs in task performance, model size, and inference speed.

\section{Research question and methodology}\label{sec:methodology}

\subsection{Research question}

The main research question is:


To what extent can a compact Transformer model imitate a larger LLM teacher for toxic comment classification.
What are the trade offs between predictive performance, model size, and inference speed?


This question is task specific. 
The goal is not to show that a small model can replace a general purpose LLM in reasoning or conversation. 
The project studies if the teacher's decision behaviour can be compressed into a smaller model for one domain specific classification problem.

\subsection{Problem definition}

Let $x_i$ be a text comment and let $y_i \in \{0,1\}$ be its original dataset label, where $0$ denotes not toxic and $1$ denotes toxic. 
The supervised baseline learns a classifier
\begin{equation}
    f_{\theta}(x_i) \rightarrow \hat{y}_i,
\end{equation}
using the original dataset labels. 


In the teacher labelling stage, a large language model teacher $T$ assigns a new label $\tilde{y}_i \in \{0,1\}$ to each selected example of the data and confidence scores $p_T(y=0|x_i)$ and $p_T(y=1|x_i)$. 
The resulting teacher labelled dataset is
\begin{equation}
    \mathcal{D}_T = \{(x_i, \tilde{y}_i)\}_{i=1}^{N}.
\end{equation}

The distilled student $S_{\phi}$ is trained to imitate the teacher labels. In this implementation, I use hard-label distillation, where the loss is standard cross-entropy computed against the teacher label:
\begin{equation}
    \mathcal{L}_{distill}
    =
    \mathcal{L}_{CE}(\tilde{y}_i, p_S(x_i)).
\end{equation}

This differs from classical soft label distillation, where the student is trained to match the full teacher probability distribution. 
It can be implemented using a temperature scaled Kullback--Leibler divergence loss.
A common formulation is

\begin{equation}
    \mathcal{L} = (1 - \alpha)\,\mathcal{L}_{CE}(y, p_S) + \alpha \tau^2\,\mathcal{L}_{KL}(p_T^{(\tau)}, p_S^{(\tau)}),
\end{equation}
where $\mathcal{L}_{CE}$ is cross entropy with hard labels, $\mathcal{L}_{KL}$ is the Kullback--Leibler divergence between teacher and student probability distributions, $\tau$ is the distillation temperature, and $\alpha$ controls the trade off between the two terms.
Soft label distillation is considered as future work in this project.
In this project the implemented experiment focuses on hard label teacher imitation.

\subsection{Pipeline overview}

The project pipeline consists of five stages:

\begin{enumerate}
    \item \textbf{Data preparation.} The dataset is loaded from Hugging Face and converted into reproducible train, validation, and test CSV splits. 
    The main supervised experiments use natural-distribution stratified splits that preserve the original class imbalance.
    \item \textbf{Baseline models.} A TF-IDF and Logistic Regression model is trained as a baseline. 
    A BERT-tiny model is then finetuned on the original labels as a supervised Transformer baseline.
    \item \textbf{Supervised local teacher.} A BERT-base model is finetuned on the natural distribution original labels.
    It is used to produce logits and probabilities for later soft-label distillation.
    \item \textbf{Teacher labelling.} An OpenAI LLM teacher labels a stratified subset of examples and returns a binary label, confidence scores, and a short reason. 
    This step produces a teacher labelled dataset for distillation.
    \item \textbf{Distilled student.} Train a distilled BERT-tiny student on teacher labels, initialized from the supervised BERT-tiny run. 
    Evaluate quality metrics and benchmark model size and inference speed.
\end{enumerate}

The implementation is organised as a Python package.
Separate modules are used for data loading, preprocessing, baseline models, Transformer training, teacher prompting, evaluation, and benchmarking. 

\section{Experimental results}\label{sec:results}

\subsection{Dataset and preprocessing}

The experiments use the \texttt{SetFit/toxic\_conversations} dataset from Hugging Face.
The dataset contains comments labelled as toxic or not toxic and the columns \texttt{text}, \texttt{label}, and \texttt{label\_text}. 
The full dataset contains more than 1.7 million training examples and 50,000 test examples.
The original distribution is highly imbalanced, with around 8\% toxic examples. 
The main original-label experiments use natural distribution stratified splits.
The training and validation splits are sampled from the original Hugging Face training split, while the test split is sampled from the original Hugging Face test split.
The resulting splits preserve the natural class imbalance as closely as possible: 10,000 training examples, 2,000 validation examples, and 3,000 test examples.
The toxic class represents 8.00\% of the train and validation splits and 7.90\% of the test split, as shown in Table~\ref{tab:natural-splits}.
For OpenAI teacher labeling, final deterministic teacher label splits were created from already labeled examples. 
Their distributions are reported in Table~\ref{tab:teacher-agreement}.

\begin{table}[h]
\caption{Natural-distribution stratified splits used for the main original-label experiments.}\label{tab:natural-splits}
\centering
\begin{tabular}{lrrrr}
\toprule
Split & Rows & Label 0 & Label 1 & Toxic \% \\
\midrule
Train & 10000 & 9200 & 800 & 8.00 \\
Validation & 2000 & 1840 & 160 & 8.00 \\
Test & 3000 & 2763 & 237 & 7.90 \\
\bottomrule
\end{tabular}
\end{table}

Preprocessing was intentionally minimal.
Handled empty values, leading and trailing spaces were removed, and repeated spaces were normalised. 
No lowercasing or punctuation removal was applied, because Transformer tokenizers are designed to process raw text.
In the separate OpenAI teacher-labelled subset, the selected original labels follow a controlled 70\% not toxic and 30\% toxic distribution.
The OpenAI teacher consistently assigns more examples to the toxic class than the original annotations, with a distribution closer to 55\% not toxic and 45\% toxic.
This shows that the OpenAI teacher applies a stricter toxicity boundary, especially for hostile or aggressive comments originally labelled as not toxic.

\subsection{Evaluation metrics}

The main classification metrics are accuracy, precision, recall, F1 score, and the confusion matrix. 
Because the task is class imbalanced, F1 score is treated as more informative than accuracy measure.
In addition, model compactness and computational cost are evaluated using model size on disk, average inference time per example, and examples processed per second on CPU.

\subsection{Classical baseline and supervised BERT-base teacher}

The first baseline is a classical TF-IDF and Logistic Regression classifier.
It represents the vector space and linear classification part of the NLP course.
This baseline was retrained on the natural distribution split.
It was using unigram and bigram TF-IDF features, a maximum of 20,000 features, and balanced Logistic Regression.
The local supervised teacher is a pretrained \texttt{bert-base-uncased} model.
It's finetuned on the same natural distribution original labels.
It is important to distinguish this from BERT pretraining.
The model is not trained from scratch, but finetuned for toxic comment classification.
Because the dataset is imbalanced, the BERT-base training uses weighted cross-entropy with class weights computed from the training distribution.

For both models, a default threshold of 0.5 was evaluated.
In addition, the range of thresholds from 0.05 to 0.95 was checked on the validation set.
And the threshold with the best validation F1 was selected.
The selected threshold was then evaluated once on the test set.
Threshold tuning is validation based and does not use test labels for model selection.

Table~\ref{tab:natural-baselines} shows the test results on the 3,000 example natural distribution test split.

\begin{table}[h]
\caption{Performance on the natural-distribution 3,000 example test split.}\label{tab:natural-baselines}
\centering
\begin{tabular}{lrrrrr}
\toprule
Model & Threshold & Accuracy & Precision & Recall & F1 \\
\midrule
TF-IDF + Logistic Regression & 0.50 & 0.8967 & 0.3719 & 0.4473 & 0.406 \\
TF-IDF + Logistic Regression & 0.52 & 0.9020 & 0.3874 & 0.4135 & 0.400 \\
BERT-base supervised teacher & 0.50 & 0.9313 & 0.5508 & 0.7089 & 0.620 \\
BERT-base supervised teacher & 0.49 & 0.9303 & 0.5452 & 0.7131 & 0.618 \\
\bottomrule
\end{tabular}
\end{table}

The BERT-base supervised teacher substantially improves over the TF-IDF baseline on the natural test split.
At the default threshold, BERT-base reaches an F1 score of 0.62, compared with 0.4061 for TF-IDF.
The improvement comes mainly from much higher recall on the toxic class.
The TF-IDF model detects 106 of 237 toxic test examples at threshold 0.5, while BERT-base detects 168 of 237.
The validation-selected thresholds are close to 0.5 for both models.
For TF-IDF, validation tuning selected 0.52, improving validation F1 from 0.4348 to 0.4444, but test F1 decreased slightly from 0.4061 to 0.4000.
For BERT-base, validation tuning selected 0.49, improving validation F1 from 0.6154 to 0.6271, but test F1 changed only slightly from 0.62 to 0.618.
Therefore, the default threshold remains a strong operating point for the test set, while the validation tuning results are still useful for calibration analysis.

The default-threshold test confusion matrix for the TF-IDF baseline is
\begin{equation}
\begin{bmatrix}
2584 & 179 \\
131 & 106
\end{bmatrix},
\end{equation}
while the BERT-base supervised teacher obtains
\begin{equation}
\begin{bmatrix}
2626 & 137 \\
69 & 168
\end{bmatrix}.
\end{equation}
These matrices show that BERT-base reduces both false positives and false negatives compared with the TF-IDF baseline.
The finetuned BERT-base model saved in \texttt{results/bert\_base\_supervised/} matches the best validation checkpoint, that was at epoch 3 with validation F1 equal to 0.6154.
The model logits and probabilities were exported for the train, validation, and test splits for future soft-label distillation.

The BERT-base validation curve is reported in Table~\ref{tab:bert-base-history}.
The model reaches its best validation F1 at epoch 3.
After that point, training loss continues to decrease but validation loss increases, which indicates mild overfitting.

\begin{table}[h]
\caption{BERT-base supervised teacher validation history.}\label{tab:bert-base-history}
\centering
\begin{tabular}{rrrrr}
\toprule
Epoch & Train loss & Validation loss & Validation accuracy & Validation F1 \\
\midrule
1 & 0.4127 & 0.3104 & 0.9295 & 0.6137 \\
2 & 0.2118 & 0.3221 & 0.8630 & 0.5000 \\
3 & 0.1166 & 0.3505 & 0.9325 & 0.6154 \\
4 & 0.0687 & 0.6382 & 0.9275 & 0.5983 \\
5 & 0.0436 & 0.8335 & 0.9390 & 0.5987 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]
\caption{Validation threshold tuning summary for the natural distribution experiment.}\label{tab:threshold-tuning}
\centering
\small
\begin{tabular}{@{}lrrrr@{}}
\toprule
Model & Threshold & Val. F1 & Test F1 0.5 & Test F1 tuned \\
\midrule
TF-IDF + Logistic Regression & 0.52 & 0.4444 & 0.406 & 0.400 \\
BERT-base supervised teacher & 0.49 & 0.6271 & 0.620 & 0.618 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Teacher labelling analysis}

An OpenAI LLM teacher was used to label controlled stratified subsets of the data.
The teacher prompt defined toxicity as insults, harassment, threats, hate, severe disrespect, or abusive language.
It also stated that comments may be negative, political, or disagreeable without necessarily being toxic.
The teacher returned a binary label, confidence scores, and a short reason.
On the final teacher label test split, agreement between original and teacher labels is 0.8033.
Table~\ref{tab:teacher-agreement} summarises the current teacher labelled subset.

\begin{table}[ht]
\caption{Agreement between original dataset labels and OpenAI teacher labels on the final teacher-labelled splits.}
\label{tab:teacher-agreement}
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
Split & Rows & Original 0 & Original 1 & Teacher 0 & Teacher 1 & Agreement \\
\midrule
Train & 1500 & 1050 & 450 & 816 & 684 & 0.7627 \\
Validation & 300 & 210 & 90 & 160 & 140 & 0.7733 \\
Test & 300 & 210 & 90 & 167 & 133 & 0.8033 \\
\botrule
\end{tabular}
\end{table}

Two main disagreement patterns were observed:
\begin{itemize}
\item Original label 0, teacher label 1: comments that were originally annotated as non-toxic but contained hostile, demeaning, insulting, or identity-related language.
\item Original label 1, teacher label 0: comments that contained sensitive, political, or negative terms, but did not necessarily contain direct harassment or abuse under the prompt definition.
\end{itemize}

The teacher agrees with the original labels on 76.27\% of the train split, 77.33\% of the validation split, and 80.33\% of the test split. 
The teacher labels a higher proportion of examples as toxic than the original dataset.
This suggests that the teacher uses a stricter decision boundary for hostile language.
For example, comments originally labelled as non-toxic but containing phrases such as ``you do not have a clue'', ``vile race baiting hate propaganda'', or ``more yapping from someone who knows nothing'' were often labelled as toxic by the teacher. 
Some comments originally labelled toxic were considered non-toxic by the teacher when they contained mild profanity or negative language without direct abuse.

This confirms that the LLM teacher should not be treated as a gold standard.
Instead, it defines a different decision boundary. 
The distillation task is therefore best interpreted as teacher imitation, not a direct optimization of the original dataset labels.

\subsection{Distilled student results}

The first distillation attempt was trained from the base BERT-tiny model on a smaller teacher labeled set.
It predicted too few toxic examples and performed poorly. 
The final approach improved this by using more teacher labeled examples and initializing the distilled model from the supervised BERT-tiny checkpoint. 
The resulting model was then finetuned on OpenAI teacher labels.

Table~\ref{tab:distilled-results} reports the final distilled student results.
The model is evaluated in comparison to two cases.
First, against teacher labels that measures teacher imitation.
Second, against original labels, that measures compatibility with the original dataset annotations.

\begin{table}[h]
\caption{Final distilled BERT-tiny results on the teacher labeled validation and test subsets.}\label{tab:distilled-results}
\centering
\begin{tabular}{llrr}
\toprule
Split & Evaluation target & Accuracy & F1 \\
\midrule
Validation & Teacher labels & 0.743 & 0.759 \\
Test & Teacher labels & 0.703 & 0.696 \\
Test & Original labels & 0.707 & 0.648 \\
\bottomrule
\end{tabular}
\end{table}

The distilled student reaches an F1 score of 0.696 against the teacher on the final test subset.
This indicates that the compact model partially reaches the teacher's decision boundary.
Against the original labels on the teacher-labelled test subset, its F1 score is 0.6480.
This is close to the supervised BERT-tiny result of 0.6582 obtained on the larger 1000-example original-label test split.
But the two numbers are not perfectly comparable because they are computed on different test subsets.
This is expected because the distilled student is optimized for teacher imitation, and the teacher disagrees with the original labels on approximately 20\% of the final teacher labeled test subset.

The prediction distribution also shows a limitation.
On the final test subset, the original labels contain 210 non-toxic and 90 toxic examples.
The teacher labels contain 167 non-toxic and 133 toxic examples.
The distilled model predicts 140 non-toxic and 160 toxic examples.
Therefore, the student successfully moves toward the teacher's stricter toxicity boundary.
But it slightly overpredicts the toxic class compared with the teacher.

\subsection{Efficiency benchmark}

Efficiency was measured on CPU using the test split.
The benchmark includes model size on disk, average inference time per example, and throughput in examples per second.
Results are shown in Table~\ref{tab:benchmark}.

\begin{table}[h]
\caption{CPU efficiency benchmark for locally deployable models}\label{tab:benchmark}
\centering
\begin{tabular}{lrrr}
\toprule
Model & Size (MB) & Time per example (ms) & Examples per sec \\
\midrule
TF-IDF and Logistic Regression & 0.89 & 0.0611 & 16379.73 \\
BERT-tiny supervised student & 17.42 & 1.6061 & 622.61 \\
BERT-tiny distilled student & 17.42 & 1.5578 & 641.94 \\
\bottomrule
\end{tabular}
\end{table}

The TF-IDF baseline is approximately 19.6 times smaller than the BERT-tiny models and more than 25 times faster on CPU.
However, its original label F1 score is lower than the supervised BERT-tiny model.
The supervised and distilled BERT-tiny models have almost identical size and speed.
It's expected, because they share the same architecture.
Their difference is the decision boundary learned during training.
The supervised model follows the original labels, while the distilled model adapts to the teacher labels.

\begin{table}[h]
\caption{Practical comparison between the OpenAI teacher and the distilled student.}
\label{tab:teacher-student-efficiency}
\centering
\begin{tabular}{lrrr}
\toprule
Model & Deployment & Time per example & Examples per sec \\
\midrule
OpenAI LLM teacher & Remote API & 5440 ms & 0.18 \\
BERT-tiny distilled student & Local CPU & 1.5578 ms & 641.94 \\
\bottomrule
\end{tabular}
\end{table}

The OpenAI teacher is not directly comparable to the local models in terms of model size.
Because it is accessed through a proprietary remote API and its internal parameters and serving hardware are not observable.
However, the practical labelling time can be estimated from the teacher labelling runs.
Labelling 2100 examples took approximately 3.17 hours, corresponding to about 5.44 seconds per example, or 0.18 examples per second.
In contrast, the distilled BERT-tiny student runs locally on CPU at 1.5578 ms per example, or 641.94 examples per second.
Therefore, the distilled student is approximately 3500 times faster in the measured deployment setting.

This comparison illustrates the motivation for distillation.
The OpenAI teacher is useful for producing high-level labels, confidence scores, and short explanations.
But it is costly and slow to query repeatedly.
The distilled student does not reproduce the full capabilities of the LLM, but it provides a compact local approximation of the teacher's behaviour on the selected toxicity classification task.

\section{Concluding Remarks}\label{sec:conclusion}

In this project a complete apprentice model pipeline was implemented and evaluated for toxic comment classification.
The results show that a compact BERT-tiny student can be adapted to imitate an LLM teacher on a narrow NLP task.
On the natural distribution original-label experiment, the classical TF-IDF and Logistic Regression baseline reached an F1 score of 0.406 on the test split at the default threshold.
The finetuned BERT-base supervised teacher reached an F1 score of 0.62 on the same test split.
This confirms that contextual Transformer representations provide a high improvement over the classical sparse vector baseline for this imbalanced toxicity task.
The final distilled model achieved an F1 score of 0.696 against teacher labels, demonstrating partial transfer of the teacher's decision behaviour.
At the same time, the distilled model did not improve performance against the original dataset labels compared with the supervised BERT-tiny baseline.
Because the teacher applies a different and stricter interpretation of toxicity, optimizing for teacher imitation naturally changes the evaluation behaviour.

The experiments also highlight important tradeoffs.
The TF-IDF baseline is extremely efficient and interpretable, but weaker in F1 score.
BERT-tiny and BERT-base provide better classification quality, but are significantly larger and slower.
The OpenAI teacher, on the other hand, is powerful and can provide labels, confidence scores, and short explanations.
But it is accessed through a remote API and is expensive and slow to query repeatedly.
In the measured labelling pipeline, the OpenAI teacher required approximately 5.44 seconds per example, while the distilled BERT-tiny student performed local CPU inference in 1.5578 ms per example.
This illustrates the practical motivation for distillation: expensive teacher decisions can be used offline to train a compact local model that is much faster at deployment time.
Distillation does not change model size or speed because the architecture remains the same, but it changes the decision boundary of the student.
This supports the idea that knowledge distillation can be used not only for compression, but also for task specific behavioural adaptation.

There are several limitations.
First, the project uses hard label distillation, not a classical soft label distillation with temperature and KL-divergence.
This loses information contained in the teacher's probability distribution.
Second, the OpenAI teacher is not an objective ground truth and may be sensitive to prompt wording.
Third, the final teacher labeled dataset is smaller than the original supervised training set because API labeling has cost and time constraints.
Finally, the validation threshold tuning experiments did not improve test F1 for either TF-IDF or BERT-base.
This means that threshold calibration should be interpreted carefully.
The distilled student also slightly overpredicts the toxic class compared with the teacher.
It shows that soft label training could improve calibration.

Future work could extend the project in several directions.
The most direct extension is soft label distillation using teacher probabilities and a KL-divergence loss.
Another extension is to distil the BERT-base teacher logits exported from the natural-distribution experiment into BERT-tiny.
Additional work could compare multiple teachers, such as an OpenAI LLM and an open-source toxicity classifier.
Or include explanation based distillation.
Finally, a larger teacher labelled dataset would allow a more reliable evaluation of generalization and teacher imitation.

\begin{thebibliography}{9}

\bibitem{hinton2015distilling}
Hinton, G., Vinyals, O., Dean, J.: Distilling the knowledge in a neural network. arXiv preprint arXiv:1503.02531 (2015)

\bibitem{devlin2019bert}
Devlin, J., Chang, M.-W., Lee, K., Toutanova, K.: BERT: Pre-training of deep bidirectional transformers for language understanding. In: Proceedings of NAACL-HLT, pp. 4171--4186 (2019)

\bibitem{jiao2020tinybert}
Jiao, X., Yin, Y., Shang, L., Jiang, X., Chen, X., Li, L., Wang, F., Liu, Q.: TinyBERT: Distilling BERT for natural language understanding. In: Findings of the Association for Computational Linguistics: EMNLP 2020, pp. 4163--4174 (2020)

\end{thebibliography}

\end{document}
